**The Mint Scale: A Fresh Validation of the Multimodal Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS**

### 2025-08-22 paper/manuscript.qmd
update

numbered-lines: false

@@

mask: false

@@

Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list is available at [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)]. We additionally crafted 8 "attention check" items blending in (and distributed across) each category.

@@

For both studies, data analysis was carried out using R [4.4.3, @Rcoreteam], leveraging the *easystats* ecosystem [@ludecke2019insight; @ludecke2020extracting] and the *EGAnet* package [@christensen2021estimating]. The reproducible code and additional details are available at https://github.com/RealityBending/InteroceptionScale.

@@

In order to avoid the repetition of similar types of questions and and balance longer and shorter questionnaires, we partitioned the measures into three groups (and randomized the order within them): 1) interoception questionnaires (MAIA, IAS, BPQ), 2) emotions (TAS, CERQ, ERS, PI-18), and 3) health (somatic symptoms, mental health, LS + PHQ-4, CEFSA). 
After completing demographic questions, participants always started with the Mint scale, and each following interoception questionnaire was interspersed with two questionnaires from the emotions and pathology groups. 7 attention checks were embedded throughout (one within each major questionnaire).
In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on https://github.com/RealityBending/InteroceptionScale].

@@

Data, code, and all materials are available at https://github.com/RealityBending/InteroceptionScale.

# Acknowledgements

We would like to thank Hugo Critchley for his valuable feedback on the manuscript.
DM would also like to thank Anastasia for the motivation provided to write this paper.

>>>>

numbered-lines: true

@@

mask: true

@@

Using this orthogonal 7x6 modality/facet grid as a conceptual scaffolding, we generated 120 initial items, striving for a balanced number of items with consistent phrasing within modalities and facets^[The initial item list is available at
<!-- [realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html](https://realitybending.github.io/InteroceptionScale/study1/analysis/2_analysis.html)] -->
*[MASKED FOR REVIEW]*
. We additionally crafted 8 "attention check" items blending in (and distributed across) each category.

@@

For both studies, data analysis was carried out using R [4.4.3, @Rcoreteam], leveraging the *easystats* ecosystem [@ludecke2019insight; @ludecke2020extracting] and the *EGAnet* package [@christensen2021estimating]. The reproducible code and additional details are available at 
*[MASKED FOR REVIEW]*.
<!-- https://github.com/RealityBending/InteroceptionScale. -->

@@

In order to avoid the repetition of similar types of questions and and balance longer and shorter questionnaires, we partitioned the measures into three groups (and randomized the order within them): 1) interoception questionnaires (MAIA, IAS, BPQ), 2) emotions (TAS, CERQ, ERS, PI-18), and 3) health (somatic symptoms, mental health, LS + PHQ-4, CEFSA). 
After completing demographic questions, participants always started with the Mint scale, and each following interoception questionnaire was interspersed with two questionnaires from the emotions and pathology groups. 7 attention checks were embedded throughout (one within each major questionnaire).
In order to make the experiment more enjoyable, the experiment ended with a radar chart summarizing the participants' responses to the Mint scale^[The experiment can be tested by following the link on 
*[MASKED FOR REVIEW]*.
<!-- https://github.com/RealityBending/InteroceptionScale]. -->

@@

Data, code, and all materials are available at 
*[MASKED FOR REVIEW]*.
<!-- https://github.com/RealityBending/InteroceptionScale. -->

<!-- # Acknowledgements -->

<!-- We would like to thank Hugo Critchley for his valuable feedback on the manuscript. -->
<!-- DM would also like to thank Anastasia for the motivation provided to write this paper. -->
